# Figure generation script, invasion risk

# ~~~~ Notes

-------------------------------------------------------------------------------

# 1.) Contact info

Contact: Steven Brownlee
Email: steven.fr.brownlee@gmail.com
Date last revised: March 17 2025

-------------------------------------------------------------------------------

# 2.) Session info

## Steven 

R version 4.4.3 (2025-02-28)
Platform: x86_64-redhat-linux-gnu
Running under: Nobara Linux 41 (GNOME Edition)

Matrix products: default
BLAS/LAPACK: FlexiBLAS OPENBLAS-OPENMP;  LAPACK version 3.12.0

locale:
 [1] LC_CTYPE=en_CA.UTF-8      LC_NUMERIC=C              LC_TIME=en_CA.utf8        LC_COLLATE=en_CA.UTF-8   
 [5] LC_MONETARY=en_CA.utf8    LC_MESSAGES=en_CA.UTF-8   LC_PAPER=en_CA.utf8       LC_NAME=C                
 [9] LC_ADDRESS=C              LC_TELEPHONE=C            LC_MEASUREMENT=en_CA.utf8 LC_IDENTIFICATION=C      

time zone: America/Vancouver
tzcode source: system (glibc)

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base     

other attached packages:
 [1] ggtext_0.1.2      cubelyr_1.0.2     ggdist_3.3.2      BAMMtools_2.1.12  ape_5.8-1         ambient_1.0.2    
 [7] colorspace_2.1-1  ggpattern_1.1.4   patchwork_1.3.0   ggnewscale_0.5.0  tidyterra_0.7.0   terra_1.8-21     
[13] rcartocolor_2.1.1 extrafont_0.19    lubridate_1.9.4   forcats_1.0.0     stringr_1.5.1     dplyr_1.1.4      
[19] purrr_1.0.4       readr_2.1.5       tidyr_1.3.1       tibble_3.2.1      ggplot2_3.5.1     tidyverse_2.0.0  
[25] ncmeta_0.4.0      stars_0.6-8       sf_1.0-19         abind_1.4-8      

loaded via a namespace (and not attached):
 [1] gtable_0.3.6         xfun_0.50            caTools_1.18.3       lattice_0.22-6       tzdb_0.4.0          
 [6] bitops_1.0-9         vctrs_0.6.5          tools_4.4.3          generics_0.1.3       parallel_4.4.3      
[11] proxy_0.4-27         pkgconfig_2.0.3      KernSmooth_2.23-26   distributional_0.5.0 lifecycle_1.0.4     
[16] compiler_4.4.3       farver_2.1.2         gplots_3.2.0         munsell_0.5.1        codetools_0.2-20    
[21] htmltools_0.5.8.1    class_7.3-23         yaml_2.3.10          Rttf2pt1_1.3.12      pillar_1.10.1       
[26] extrafontdb_1.0      classInt_0.4-11      RNetCDF_2.9-2        nlme_3.1-167         gtools_3.9.5        
[31] tidyselect_1.2.1     digest_0.6.37        stringi_1.8.4        fastmap_1.2.0        grid_4.4.3          
[36] cli_3.6.4            magrittr_2.0.3       e1071_1.7-16         withr_3.0.2          scales_1.3.0        
[41] timechange_0.3.0     rmarkdown_2.29       hms_1.1.3            evaluate_1.0.3       knitr_1.49          
[46] rlang_1.1.5          gridtext_0.1.5       Rcpp_1.0.14          glue_1.8.0           DBI_1.2.3           
[51] xml2_1.3.6           rstudioapi_0.17.1    R6_2.6.1             units_0.8-5  

-------------------------------------------------------------------------------

# 3.) R library setup

Optional code to install packages if not already installed:

```{r}
#install.packages(c('stars', 'ncmeta', 'tidyverse', 'extrafont', 'sf', 'rcartocolor',  
#'terra', 'tidyterra', 'ggnewscale', 'patchwork', 'ggpattern', 'colorspace',
#'ambient', 'BAMMtools', 'ggdist', 'cubelyr', 'ggtext'))

```

```{r}
library(stars)
library(ncmeta)
library(tidyverse)
library(extrafont)
library(svglite)
library(sf)
library(rcartocolor)
library(terra)
library(tidyterra)
library(ggnewscale)
library(patchwork)
library(ggpattern)
library(colorspace)
library(ambient)
library(BAMMtools)
library(ggdist)
library(cubelyr)
library(ggtext)
library(rphylopic)
library(patchwork)
library(googledrive)
library(future)
library(future.callr)
library(purrr)
library(furrr)
library(paletteer)

```


-------------------------------------------------------------------------------

# 4.) Directory setup

## Steven

```{r setup,include=FALSE}
knitr::opts_knit$set(root.dir = '/home/steven/Documents/workspace/thesis/ch1/gis_data/')
```

## Set path for export of figures:

```{r}
figure_path = 'figures/'
```

-------------------------------------------------------------------------------

