
# Spatial analysis script, invasion risk

# Contact information

Contact: Steven Brownlee
Email: steven.fr.brownlee@gmail.com
Date last revised: June 24 2024

# Session info

R version 4.4.1 (2024-06-14)
Platform: x86_64-redhat-linux-gnu
Running under: Nobara Linux 40 (GNOME Edition)

Matrix products: default
BLAS/LAPACK: FlexiBLAS OPENBLAS-OPENMP;  LAPACK version 3.11.0

locale:
 [1] LC_CTYPE=en_CA.UTF-8      LC_NUMERIC=C              LC_TIME=en_CA.utf8       
 [4] LC_COLLATE=en_CA.UTF-8    LC_MONETARY=en_CA.utf8    LC_MESSAGES=en_CA.UTF-8  
 [7] LC_PAPER=en_CA.utf8       LC_NAME=C                 LC_ADDRESS=C             
[10] LC_TELEPHONE=C            LC_MEASUREMENT=en_CA.utf8 LC_IDENTIFICATION=C      

time zone: America/Vancouver
tzcode source: system (glibc)

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base     

loaded via a namespace (and not attached):
 [1] digest_0.6.36     tidyr_1.3.1       utf8_1.2.4        R6_2.5.1         
 [5] fastmap_1.2.0     tidyselect_1.2.1  xfun_0.46         magrittr_2.0.3   
 [9] glue_1.7.0        tibble_3.2.1      knitr_1.48        pkgconfig_2.0.3  
[13] htmltools_0.5.8.1 rmarkdown_2.27    dplyr_1.1.4       generics_0.1.3   
[17] lifecycle_1.0.4   cli_3.6.3         fansi_1.0.6       vctrs_0.6.5      
[21] compiler_4.4.1    purrr_1.0.2       rstudioapi_0.16.0 tools_4.4.1      
[25] pillar_1.9.0      evaluate_0.24.0   yaml_2.3.10       rlang_1.1.4   

# Set up data directory

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = '/home/steven/Documents/workspace/thesis/ch1/gis_data/')
```

# R library setup

```{r}
library(sf)
library(tidyverse)
library(rcartocolor)
library(sfnetworks)
library(qgisprocess)
library(future)
library(future.callr)
library(purrr)
library(furrr)
library(progressr)
library(stars)
library(paletteer)
library(ggnewscale)
library(terra)
library(tidyterra)
library(imputeTS)

```

# Set up Python

```{r Python setup}

install.packages("reticulate")

library(reticulate)

install_miniconda(path = miniconda_path(), update = T)

reticulate::install_python()

reticulate::virtualenv_create(envname = 'cci_lakes')

use_virtualenv('cci_lakes')

reticulate::py_install(packages = c('xarray', 'dask', 'netCDF4', 'bottleneck', 
                                    'rasterio', 'pyproj', 'geopandas', 'pandas', 
                                    'cartopy', 'distributed', 'numpy',
                                    'datetime'))

```

# Import common files

```{r}

bc_bbox <- vect('auxiliary_files/bc_bbox.gpkg')

cci_lakes_outline <- vect('auxiliary_files/cci_lakes_shapefile.gpkg')

cci_lakes_outline_sf <- read_sf('auxiliary_files/cci_lakes_shapefile.gpkg')

```


# 1.) Download files from CCI database.


```{r}

path = 'cci_lakes_download/'

###

prefix_template <- 'https://dap.ceda.ac.uk/neodc/esacci/lakes/data/lake_products/L3S/v2.1/merged_product/'

suffix_template_a <- 'ESACCI-LAKES-L3S-LK_PRODUCTS-MERGED-'

suffix_template_b <- '-fv2.1.0.nc'

###

year_list <- c('2016', '2017', '2018', '2019', '2020')

month_list <- c('01', '02', '03', '04', '05', '06', '07', '08', '09', '10', '11', '12')

month_daylengths <- c(31, 28, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31)

day_list <- c( '01',  '02',  '03',  '04',  '05',  '06',  '07',  '08',  '09', 
               '10', '11', '12', '13',  '14', '15', '16', '17', '18', '19', 
               '20',  '21', '22', '23', '24', '25', '26', '27', '28', '29', 
               '30', '31')

comb_date <- paste0(year_list[1], month_list[1], day_list[1])

date_dir <- paste0(year_list[1], '/', month_list[1], '/')

for (i in 1:5) {
  ival <- eval(i)
  
  interior_year <- year_list[ival]
  
  for (j in 1:12) {
    jval <- eval(j)
    
    interior_month <- month_list[jval]
    
    interior_day_length <- month_daylengths[jval]
    
    if (interior_month == '02' & interior_year == '2016') {
      interior_day_length <- 29
      print('Leap year!')
    } 
    
    if (interior_month == '02' & interior_year == '2020') {
      interior_day_length <- 29
      print('Leap year!')
    }

    for (k in 1:interior_day_length) {
      kval <- eval(k)
      
      interior_day <- day_list[kval]
      
      comb_date <- paste0(interior_year,  interior_month, interior_day )
      
      date_dir <- paste0(interior_year, '/', interior_month , '/')
      
      filename <- paste0(prefix_template, date_dir, suffix_template_a, comb_date,
                              suffix_template_b)

      download.file(filename, paste0(path, basename(filename)))
      
      print(paste('Completed:', filename))
      
    }
    
  }
  
}

```

# 2.) Process .nc files and export as RDS

```{r}

cci_files <- list.files('cci_lakes_download/', 
                            pattern = '*.nc',
                            full.names = TRUE,
                            recursive = TRUE)

outdir <- 'cci_lakes_rds/'

xy_outdir <- 'cci_lakes_coords/'

for (i in 1:length(cci_files)) {
  ival <- eval(i)
  input_file <- cci_files[ival]
  input_filename <- basename(input_file)
  
  ## Extract dates from filename
  
  year_extract <- substr(input_filename, 37, 40)
  month_extract <- substr(input_filename, 41, 42)
  date_extract <- substr(input_filename, 43, 44)
  composite_date <- paste0(date_extract, '-', month_extract, '-', year_extract)
 
  ## Extract data from file
  
  interior_terra <- rast(input_file)
  
  chla_mean <- interior_terra %>% 
  select(chla_mean) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()
  
  chla_mean_coords <- chla_mean  %>% 
  select(x, y)
  
  ##
  
  chla_uncertainty <- interior_terra %>% 
  select(chla_uncertainty) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()
  
  chla_uncertainty_coords <- chla_uncertainty  %>% 
  select(x, y)
  
  ##
  
  lake_surface_water_temperature <- interior_terra %>% 
  select(lake_surface_water_temperature) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()
  
  lake_surface_water_temperature_coords <- lake_surface_water_temperature %>% 
  select(x, y)
  
  ##
  
  lswt_uncertainty <- interior_terra %>% 
   select(lswt_uncertainty) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()
  
  lswt_uncertainty_coords <- lswt_uncertainty %>% 
   select(x, y)
  
  ##
 
  lswt_quality_level <- interior_terra %>% 
   select(lswt_quality_level) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()
  
  lswt_quality_coords <- lswt_quality_level %>% 
    select(x, y) 
  
  ##
  
  turbidity_mean <- interior_terra %>% 
   select(turbidity_mean) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()
  
  tm_coords <- turbidity_mean %>% 
   select(x, y)
  
  ##
  
  turbidity_uncertainty <- interior_terra %>% 
   select(turbidity_uncertainty) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()
  
  tu_coords <- turbidity_uncertainty %>% 
   select(x, y)
  
  ##
  
  comb_table <- bind_rows(chla_mean, chla_uncertainty, 
                        lake_surface_water_temperature, lswt_uncertainty, 
                        lswt_quality_level, turbidity_mean, turbidity_uncertainty)
  
  coord_template <- bind_rows(chla_mean_coords, chla_uncertainty_coords, 
                              lake_surface_water_temperature_coords, 
                              lswt_uncertainty_coords, lswt_quality_coords, 
                              tm_coords, tu_coords) %>% 
  distinct(x, y)
  
  ##
  
  coord_filling <- left_join(coord_template, chla_mean)
  
  coord_filling <- left_join(coord_filling, chla_uncertainty)
  
  coord_filling <- left_join(coord_filling, lake_surface_water_temperature)
  
  coord_filling <- left_join(coord_filling, lswt_uncertainty)
  
  coord_filling <- left_join(coord_filling, lswt_quality_level)
  
  coord_filling <- left_join(coord_filling, turbidity_mean)
  
  coord_filling <- left_join(coord_filling, turbidity_uncertainty)
  
  ##
  
  interior_data_filled <- coord_filling %>%
    mutate(date = composite_date) %>% 
    replace(is.na(.), 0) %>% 
    mutate(na_test = chla_mean + chla_uncertainty 
           + lswt_uncertainty + lswt_quality_level 
           + turbidity_mean + turbidity_uncertainty) %>% 
    filter(na_test != 0)
  
  # Prep for export 
  
  output_filename <- paste0(outdir, 'cci_lakes_', composite_date, '_processed.rds')
  
  write_rds(interior_data_filled, output_filename)
  
  print(paste('Completed:', ival, 'of', length(cci_files)))
}
  

```

# 3.) Read .rds files, process into stars objects

```{r}

## Read data in to R, collate into one table

cci_data <- list.files('cci_lakes_rds/', 
                            pattern = '*.rds',
                            full.names = TRUE,
                            recursive = TRUE)

cci_data_collated <- lapply(cci_data, readRDS) %>% 
  bind_rows()

## Filter out unique coordinates, genereate UIDs for each

cci_unique_coordinates <- cci_data_collated %>% 
  select(x, y) %>% 
  distinct() %>% 
  st_as_sf(coords = c('x', 'y'),
           crs = 4326) %>% 
    mutate(x = sf::st_coordinates(.)[,1],
                y = sf::st_coordinates(.)[,2]) %>% 
  rowid_to_column('point_id') %>% 
  st_drop_geometry()

## Set up date sequence to pair with coordinates - need 'sequence points' to
#~ avoid annoying inability to make date columns in empty tibble

date_sequence <- seq(dmy('01-01-2016'), dmy('31-12-2020'), by = 'day') %>% 
  as_tibble() %>% 
  rename(date = value) %>% 
  rowid_to_column('date_id')

date_sequence_points <- seq(1, nrow(date_sequence), by = 1) %>% 
  as_tibble() %>% 
  rename(date_id = value)

## Append time sequences to each coordinate

coord_time_template <- tibble(point_id = numeric(),
                              x = numeric(),
                              y = numeric(),
                              date_id = numeric())

for (i in 1:max(cci_unique_coordinates$point_id)) {
  ival = eval(i)
  date_interior <- date_sequence_points %>% mutate(point_id = ival)
  coord_interior <- cci_unique_coordinates %>% filter(point_id == ival)
  interior_join <- left_join(coord_interior, date_interior, by = 'point_id')
  coord_time_template <- bind_rows(coord_time_template, interior_join)
  print(paste('Completed:', ival, 'of', max(cci_unique_coordinates$point_id)))
}

write_rds(coord_time_template, 'auxiliary_files/coord_time_template.rds')

coord_time_template <- readRDS('auxiliary_files/coord_time_template.rds')

coord_time_scaffold <- coord_time_template

coord_time_scaffold <- left_join(coord_time_scaffold, date_sequence,
                                 by = 'date_id')

## Join CCI lakes data to the scaffold

cci_data_collated$date <- dmy(cci_data_collated$date)

coord_time_joined <- left_join(coord_time_scaffold, cci_data_collated,
                               by = c('x', 'y', 'date')) %>% 
  select(-na_test)

## Export individual slices

coord_time_joined$group_id <- cut_number(coord_time_joined$point_id, 100)

coord_time_joined$group_id <- as.numeric(coord_time_joined$group_id)

test <- coord_time_joined %>% 
  filter(group_id == 5)

for (i in 1:100) {
  ival = eval(i)
  interior_subset <- coord_time_joined %>% 
  filter(group_id == ival)
  filename <- paste0('cci_lakes_slices/cci_slice_', ival, '.rds')
  write_rds(interior_subset, filename)
  print(paste('Completed:', ival, 'of', 100))
  
}


```

## Attach lake information

```{r}

cci_lakes_filtered <- cci_lakes_outline_sf %>% 
  select(id, name) %>% 
  st_make_valid()

cci_slices <- list.files('cci_lakes_slices/', 
                            pattern = '*.rds',
                            full.names = TRUE,
                            recursive = TRUE)
for (i in 1:100) {
  ###
  
  ival <- eval(i)
  
  int_slice <- readRDS(cci_slices[ival]) %>% 
    st_as_sf(coords = c('x', 'y'),
             crs = 4326)
  
  int_slice <- st_join(int_slice, cci_lakes_filtered)
  
  filename <- paste0('cci_lakes_slices_labelled/cci_slice_labelled_', ival, '.rds')
  
  write_rds(int_slice, filename)
  
  print(paste('Completed:', ival, 'of', 100))
}

cci_lakes_labelled <- list.files('cci_slices_filled/', 
                            pattern = '*.rds',
                            full.names = TRUE,
                            recursive = TRUE) %>% 
  lapply(readRDS) %>% 
  bind_rows()

total_lake_length <- length(unique(cci_lakes_labelled$name))

```


## ~3a.) Fill time series gaps

```{r}
cci_slices <- list.files('cci_lakes_slices/', 
                            pattern = '*.rds',
                            full.names = TRUE,
                            recursive = TRUE)


for (i in 1:100) {
  ###
  
  ival <- eval(i)
  
  int_slice <- readRDS(cci_slices[ival]) 
  
  ##
  
  chla <- int_slice %>% select(x, y, date, chla_mean)
  
  temp <- int_slice %>% select(x, y, date, lake_surface_water_temperature)
  
  turb <- int_slice %>% select(x, y, date, turbidity_mean)
  
  date_frame <- int_slice %>% select(x, y, date)
  
  ##
  
  chla <- chla %>% 
    group_by(x, y) %>% 
    group_modify(~ as.data.frame(na_ma(.x)), 
                 k = 4,
                 maxgap = 1826) # 1-1827, the length of the time series
  
  print(paste('Completed data frame:', ival, 'chla'))
  
  temp <- temp %>% 
    group_by(x, y) %>% 
    group_modify(~ as.data.frame(na_ma(.x)), 
                 k = 4,
                 maxgap = 1826) # 1-1827, the length of the time series
  
   print(paste('Completed data frame:', ival, 'temp'))
  
  turb <- turb %>% 
    group_by(x, y) %>% 
    group_modify(~ as.data.frame(na_ma(.x)), 
                 k = 4,
                 maxgap = 1826) # 1-1827, the length of the time series
  
  print(paste('Completed data frame:', ival, 'turb'))

  assembly_frame <- left_join(date_frame, chla)
  
  assembly_frame <- left_join(assembly_frame, temp)
  
  assembly_frame <- left_join(assembly_frame, turb)
  
  ##
  
  filename <- paste0('cci_lakes_slices_filled/cci_slice_filled_', ival, '.rds')
  
  write_rds(assembly_frame, filename)
  
  print(paste('Completed:', ival, 'of', 100))
}


test <- int_slice %>% select(x, y) %>% distinct(x, y) %>% st_as_sf(coords = c('x', 'y'), crs = 4326)

write_sf(test, '/home/steven/Downloads/test.gpkg')

```

