
# Spatial analysis script, invasion risk

# Contact information

Contact: Steven Brownlee
Email: steven.fr.brownlee@gmail.com
Date last revised: June 24 2024

# Session info

R version 4.4.1 (2024-06-14)
Platform: x86_64-redhat-linux-gnu
Running under: Nobara Linux 40 (GNOME Edition)

Matrix products: default
BLAS/LAPACK: FlexiBLAS OPENBLAS-OPENMP;  LAPACK version 3.11.0

locale:
 [1] LC_CTYPE=en_CA.UTF-8      LC_NUMERIC=C              LC_TIME=en_CA.utf8       
 [4] LC_COLLATE=en_CA.UTF-8    LC_MONETARY=en_CA.utf8    LC_MESSAGES=en_CA.UTF-8  
 [7] LC_PAPER=en_CA.utf8       LC_NAME=C                 LC_ADDRESS=C             
[10] LC_TELEPHONE=C            LC_MEASUREMENT=en_CA.utf8 LC_IDENTIFICATION=C      

time zone: America/Vancouver
tzcode source: system (glibc)

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base     

loaded via a namespace (and not attached):
 [1] digest_0.6.36     tidyr_1.3.1       utf8_1.2.4        R6_2.5.1         
 [5] fastmap_1.2.0     tidyselect_1.2.1  xfun_0.46         magrittr_2.0.3   
 [9] glue_1.7.0        tibble_3.2.1      knitr_1.48        pkgconfig_2.0.3  
[13] htmltools_0.5.8.1 rmarkdown_2.27    dplyr_1.1.4       generics_0.1.3   
[17] lifecycle_1.0.4   cli_3.6.3         fansi_1.0.6       vctrs_0.6.5      
[21] compiler_4.4.1    purrr_1.0.2       rstudioapi_0.16.0 tools_4.4.1      
[25] pillar_1.9.0      evaluate_0.24.0   yaml_2.3.10       rlang_1.1.4   

# Set up data directory

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = '/home/steven/Documents/workspace/thesis/ch1/gis_data/')
```

# R library setup

```{r}
library(sf)
library(tidyverse)
library(rcartocolor)
library(sfnetworks)
library(qgisprocess)
library(future)
library(future.callr)
library(purrr)
library(furrr)
library(progressr)
library(stars)
library(paletteer)
library(ggnewscale)
library(terra)
library(tidyterra)
library(nngeo)
library(imputeTS)
```

# Set up Python

```{r Python setup}

install.packages("reticulate")

library(reticulate)

install_miniconda(path = miniconda_path(), update = T)

reticulate::install_python()

reticulate::virtualenv_create(envname = 'cci_lakes')

use_virtualenv('cci_lakes')

reticulate::py_install(packages = c('xarray', 'dask', 'netCDF4', 'bottleneck', 
                                    'rasterio', 'pyproj', 'geopandas', 'pandas', 
                                    'cartopy', 'distributed', 'numpy',
                                    'datetime'))

```

# Import common files, process

```{r}

bc_bbox <- vect('auxiliary_files/bc_bbox.gpkg')

na_bbox <- read_sf('auxiliary_files/north_america_bbox.gpkg')

cci_lakes_outline <- vect('auxiliary_files/cci_lakes_shapefile.gpkg') 

cci_lakes_outline_sf <- read_sf('auxiliary_files/cci_lakes_shapefile.gpkg') %>% 
  st_make_valid()

wwf_glwd_1 <- read_sf('downloads/WWF_GLWD_level1/glwd_1.shp') %>% 
  st_set_crs(4326) %>% 
  select(LAKE_NAME) %>% 
  st_make_valid()

cci_lakes_joined <- st_join(cci_lakes_outline_sf, wwf_glwd_1)

cci_lakes_name_corrected <- cci_lakes_joined %>%
  mutate(name = coalesce(name, LAKE_NAME)) %>% 
  select(name, id) %>% 
  st_transform(crs = 4087) %>% 
  st_buffer(dist = 400)

write_sf(cci_lakes_name_corrected, 'auxiliary_files/cci_lakes_corrected.gpkg')

```


# 1.) Download files from CCI database.


```{r}

path = 'cci_lakes_download/'

###

prefix_template <- 'https://dap.ceda.ac.uk/neodc/esacci/lakes/data/lake_products/L3S/v2.1/merged_product/'

suffix_template_a <- 'ESACCI-LAKES-L3S-LK_PRODUCTS-MERGED-'

suffix_template_b <- '-fv2.1.0.nc'

###

year_list <- c('2016', '2017', '2018', '2019', '2020')

month_list <- c('01', '02', '03', '04', '05', '06', '07', '08', '09', '10', '11', '12')

month_daylengths <- c(31, 28, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31)

day_list <- c( '01',  '02',  '03',  '04',  '05',  '06',  '07',  '08',  '09', 
               '10', '11', '12', '13',  '14', '15', '16', '17', '18', '19', 
               '20',  '21', '22', '23', '24', '25', '26', '27', '28', '29', 
               '30', '31')

comb_date <- paste0(year_list[1], month_list[1], day_list[1])

date_dir <- paste0(year_list[1], '/', month_list[1], '/')

for (i in 1:5) {
  ival <- eval(i)
  
  interior_year <- year_list[ival]
  
  for (j in 1:12) {
    jval <- eval(j)
    
    interior_month <- month_list[jval]
    
    interior_day_length <- month_daylengths[jval]
    
    if (interior_month == '02' & interior_year == '2016') {
      interior_day_length <- 29
      print('Leap year!')
    } 
    
    if (interior_month == '02' & interior_year == '2020') {
      interior_day_length <- 29
      print('Leap year!')
    }

    for (k in 1:interior_day_length) {
      kval <- eval(k)
      
      interior_day <- day_list[kval]
      
      comb_date <- paste0(interior_year,  interior_month, interior_day )
      
      date_dir <- paste0(interior_year, '/', interior_month , '/')
      
      filename <- paste0(prefix_template, date_dir, suffix_template_a, comb_date,
                              suffix_template_b)

      download.file(filename, paste0(path, basename(filename)))
      
      print(paste('Completed:', filename))
      
    }
    
  }
  
}

```

# 2.) Process .nc files and export as RDS

```{r}


cci_files <- list.files('cci_lakes_download/', 
                            pattern = '*.nc',
                            full.names = TRUE,
                            recursive = TRUE)

outdir <- 'cci_lakes_rds/'

xy_outdir <- 'cci_lakes_coords/'

for (i in 1218:length(cci_files)) {
  ival <- eval(i)
  input_file <- cci_files[ival]
  input_filename <- basename(input_file)
  
  ## Extract dates from filename
  
  year_extract <- substr(input_filename, 37, 40)
  month_extract <- substr(input_filename, 41, 42)
  date_extract <- substr(input_filename, 43, 44)
  composite_date <- paste0(date_extract, '-', month_extract, '-', year_extract)
 
  ## Extract data from file
  
  interior_terra <- rast(input_file)
  
  t_chla_mean <- interior_terra %>% 
  select(chla_mean) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()
  
  chla_mean_coords <-  t_chla_mean  %>% 
  select(x, y)
  
  ##
  
  t_chla_uncertainty <- interior_terra %>% 
  select(chla_uncertainty) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()
  
  chla_uncertainty_coords <-  t_chla_uncertainty  %>% 
  select(x, y)
  
  ##
  
  t_lake_surface_water_temperature <- interior_terra %>% 
  select(lake_surface_water_temperature) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble() %>% 
    rename(lswt = lake_surface_water_temperature)
  
  lake_surface_water_temperature_coords <-  t_lake_surface_water_temperature %>% 
  select(x, y)
  
  ##
  
  t_lswt_uncertainty <- interior_terra %>% 
   select(lswt_uncertainty) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()
  
  lswt_uncertainty_coords <-  t_lswt_uncertainty %>% 
   select(x, y)
  
  ##
 
  t_lswt_quality_level <- interior_terra %>% 
   select(lswt_quality_level) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()
  
  lswt_quality_coords <-  t_lswt_quality_level %>% 
    select(x, y) 
  
  ##
  
  t_turbidity_mean <- interior_terra %>% 
   select(turbidity_mean) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()
  
  tm_coords <-  t_turbidity_mean %>% 
   select(x, y)
  
  ##
  
  t_turbidity_uncertainty <- interior_terra %>% 
   select(turbidity_uncertainty) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()
  
  tu_coords <-  t_turbidity_uncertainty %>% 
   select(x, y)
  
  ##
  
  t_rw_443 <- interior_terra %>% 
   select(Rw443) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble()%>% 
  rename(rw_443 = Rw443)
  
  rw_443_coords <-  t_rw_443 %>% 
   select(x, y)
  
  ###
  
  t_rw_443_u <- interior_terra %>% 
   select(Rw443_uncertainty_relative) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble() %>% 
  rename(rw_443_u = Rw443_uncertainty_relative)
  
  rw_443_u_coords <- t_rw_443_u %>% 
   select(x, y)
  
  ###
  
   t_rw_547 <- interior_terra %>% 
   select(Rw547) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble() %>% 
  rename(rw_547 = Rw547)
  
   rw_547_coords <- t_rw_547  %>% 
   select(x, y)
  
  ###
    
   
   t_rw_547_u <- interior_terra %>% 
   select(Rw547_uncertainty_relative) %>% 
  crop(bc_bbox) %>% 
  st_as_stars() %>% 
   as_tibble() %>% 
  rename(rw_547_u = Rw547_uncertainty_relative)
  
   rw_547_u_coords <- t_rw_547_u %>% 
   select(x, y)
  

   ### 
  
   
  comb_table <- bind_rows(t_chla_mean, t_chla_uncertainty, 
                        t_lake_surface_water_temperature, t_lswt_uncertainty, 
                        t_lswt_quality_level, t_turbidity_mean, t_turbidity_uncertainty,
                        t_rw_443, t_rw_443_u, t_rw_547, t_rw_547_u)
  
  coord_template <- bind_rows(chla_mean_coords, chla_uncertainty_coords, 
                              lake_surface_water_temperature_coords, 
                              lswt_uncertainty_coords, lswt_quality_coords, 
                              tm_coords, tu_coords, rw_443_coords, rw_443_u_coords, 
                              rw_547_coords, rw_547_u_coords) %>% 
  distinct(x, y)
  
  ##
  
  coord_filling <- left_join(coord_template, t_chla_mean)
  
  coord_filling <- left_join(coord_filling, t_chla_uncertainty)
  
  coord_filling <- left_join(coord_filling, t_lake_surface_water_temperature)
  
  coord_filling <- left_join(coord_filling, t_lswt_uncertainty)
  
  coord_filling <- left_join(coord_filling, t_lswt_quality_level)
  
  coord_filling <- left_join(coord_filling, t_turbidity_mean)
  
  coord_filling <- left_join(coord_filling, t_turbidity_uncertainty)
  
  coord_filling <- left_join(coord_filling, t_rw_443)
  
  coord_filling <- left_join(coord_filling, t_rw_443_u)
  
  coord_filling <- left_join(coord_filling, t_rw_547)
  
  coord_filling <- left_join(coord_filling, t_rw_547_u)
  
  ##
  
  interior_data_filled <- coord_filling %>%
    mutate(date = composite_date) %>% 
    replace(is.na(.), 0) %>% 
    mutate(na_test = chla_mean + chla_uncertainty  + lswt_uncertainty + lswt_quality_level  + lwst + turbidity_mean + turbidity_uncertainty + rw_443 + rw_443_u + rw_547 + rw_547_u) %>% 
    filter(na_test != 0)
  
  # Prep for export 
  
  output_filename <- paste0(outdir, 'cci_lakes_', composite_date, '_processed.rds')
  
  write_rds(interior_data_filled, output_filename)
  
  print(paste('Completed:', ival, 'of', length(cci_files)))
  
  gc()
}
  

```

# 3.) Read .rds files, process into stars objects

```{r}

## Read data in to R, collate into one table

cci_data <- list.files('cci_lakes_rds/', 
                            pattern = '*.rds',
                            full.names = TRUE,
                            recursive = TRUE)

cci_data_collated <- lapply(cci_data, readRDS) %>% 
  bind_rows()

## Filter out unique coordinates, genereate UIDs for each

cci_unique_coordinates <- cci_data_collated %>% 
  select(x, y) %>% 
  distinct() %>% 
  st_as_sf(coords = c('x', 'y'),
           crs = 4326) %>% 
    mutate(x = sf::st_coordinates(.)[,1],
                y = sf::st_coordinates(.)[,2]) %>% 
  rowid_to_column('point_id') %>% 
  st_drop_geometry()

## Set up date sequence to pair with coordinates - need 'sequence points' to
#~ avoid annoying inability to make date columns in empty tibble

date_sequence <- seq(dmy('01-01-2016'), dmy('31-12-2020'), by = 'day') %>% 
  as_tibble() %>% 
  rename(date = value) %>% 
  rowid_to_column('date_id')

date_sequence_points <- seq(1, nrow(date_sequence), by = 1) %>% 
  as_tibble() %>% 
  rename(date_id = value)

## Append time sequences to each coordinate

coord_time_template <- tibble(point_id = numeric(),
                              x = numeric(),
                              y = numeric(),
                              date_id = numeric())

for (i in 1:max(cci_unique_coordinates$point_id)) {
  ival = eval(i)
  date_interior <- date_sequence_points %>% mutate(point_id = ival)
  coord_interior <- cci_unique_coordinates %>% filter(point_id == ival)
  interior_join <- left_join(coord_interior, date_interior, by = 'point_id')
  coord_time_template <- bind_rows(coord_time_template, interior_join)
  print(paste('Completed:', ival, 'of', max(cci_unique_coordinates$point_id)))
}

write_rds(coord_time_template, 'auxiliary_files/coord_time_template.rds')

coord_time_template <- readRDS('auxiliary_files/coord_time_template.rds')

coord_time_scaffold <- coord_time_template

coord_time_scaffold <- left_join(coord_time_scaffold, date_sequence,
                                 by = 'date_id')

## Join CCI lakes data to the scaffold

cci_data_collated$date <- dmy(cci_data_collated$date)

coord_time_joined <- left_join(coord_time_scaffold, cci_data_collated,
                               by = c('x', 'y', 'date')) %>% 
  select(-na_test)

## Export individual slices

coord_time_joined$group_id <- cut_number(coord_time_joined$point_id, 100)

coord_time_joined$group_id <- as.numeric(coord_time_joined$group_id)

for (i in 1:100) {
  ival = eval(i)
  interior_subset <- coord_time_joined %>% 
  filter(group_id == ival)
  filename <- paste0('cci_lakes_slices/cci_slice_', ival, '.rds')
  write_rds(interior_subset, filename)
  print(paste('Completed:', ival, 'of', 100))
  
}


```


## Attach lake information

```{r}

cci_slices <- list.files('cci_lakes_slices/', 
                            pattern = '*.rds',
                            full.names = TRUE,
                            recursive = TRUE)

for (i in 1:100) {
  ###
  
  ival <- eval(i)
  
  int_slice <- readRDS(cci_slices[ival]) %>% 
    st_as_sf(coords = c('x', 'y'),
             crs = 4326) %>% 
    st_transform(4087)
  
  int_slice <- st_join(int_slice, cci_lakes_name_corrected) %>% 
        mutate(x = sf::st_coordinates(.)[,1],
                y = sf::st_coordinates(.)[,2]) %>% 
    st_drop_geometry()
    
  filename <- paste0('cci_lakes_slices_labelled/cci_slice_labelled_', ival, '.rds')
  
  write_rds(int_slice, filename)
  
  print(paste('Completed:', ival, 'of', 100))
}

cci_lakes_labelled <- list.files('cci_lakes_slices_labelled/', 
                            pattern = '*.rds',
                            full.names = TRUE,
                            recursive = TRUE) %>% 
  lapply(readRDS) %>% 
  bind_rows() %>% 
  mutate(name = ifelse(is.na(name), 'no_data', name)) %>% 
  mutate(name = str_to_lower(name))

name_list <- total_lake_length <- unique(cci_lakes_labelled$name)

for (i in 1:40) {
  
  ival <- eval(i)
  
  label_filter <- cci_lakes_labelled %>% 
    filter(name == name_list[ival])
  
  filename <- paste0('cci_lakes_by_lake/cci_', name_list[ival], '.rds')
  
  write_rds(label_filter, filename)
  
  print(paste('Completed:', ival, 'of', 40))
}



```


# 4.) Fill time series gaps

```{r}

# First pass, using k-nearest neighbour filling

date_sequence <- seq(dmy('01-01-2016'), dmy('31-12-2020'), by = 'day') 

nn_filler <- function(sequence, rds_interior) {
  
  
  outer_template <- tibble(x = numeric(),
                         y = numeric(),
                         point_id = numeric(),
                         date_id = numeric(),
                         date = date(),
                         chla_mean = numeric(),
                         chla_uncertainty = numeric(),
                         lwst = numeric(),
                         lswt_uncertainty = numeric(),
                         lswt_quality_level = numeric(),
                         turbidity_mean = numeric(),
                         turbidity_uncertainty = numeric(),
                         rw_443 = numeric(),
                         rw_443_u = numeric(),
                         rw_547 = numeric(),
                         rw_547_u = numeric(),
                         group_id = numeric(),
                         name = character(),
                         id = numeric())
  
  outer_template$date <- as.Date(outer_template$date)
  
  for (i in sequence) {
    ival = eval(i)
    date_selection <- date_sequence[ival]
    rds_filtered <- rds_interior %>% 
      filter(date == date_selection)
    point_id_filtered <- unique(rds_filtered$point_id)
    point_id_length <- length(point_id_filtered)
    
    for (j in 1:eval(point_id_length)) {
      jval <- eval(j)
      rds_point_data <- rds_filtered %>% 
        filter(point_id == point_id_filtered[j])
      rds_point <- rds_filtered %>% 
        filter(point_id == point_id_filtered[j]) %>% 
        st_as_sf(coords = c('x', 'y'),
               crs = 4087) %>% 
        select(geometry)
      
      rds_comparison <- rds_filtered %>% 
        filter(point_id != point_id_filtered[j]) %>% 
            st_as_sf(coords = c('x', 'y'),
               crs = 4087)
      
      rds_nn <- suppressWarnings(suppressMessages(st_join(rds_point, 
                                                        rds_comparison, 
                                                        st_nn, k = 5))) %>% 
        mutate(grouping_id = 1)
    
      
      rds_nn_summ <- rds_nn %>% 
        group_by(grouping_id) %>% 
        summarize(chla_mean = mean(chla_mean),
                lswt_mean = mean(lwst),
                turbidity_mean = mean(turbidity_mean),
                rw_443_mean = mean(rw_443),
                rw_547_mean = mean(rw_547)) %>% 
        st_drop_geometry()
      
      eval_criteria <- rds_point_data %>% 
        select(chla_mean, lwst, turbidity_mean,
               rw_443, rw_547) 
      
      if (is.na(eval_criteria$chla_mean) == TRUE) {
        rds_point_data$chla_mean <- rds_nn_summ$chla_mean
        }
      
      if (is.na(eval_criteria$lwst) == TRUE) {
        rds_point_data$lwst <- 
          rds_nn_summ$lswt_mean
        }
      if (is.na(eval_criteria$turbidity_mean) == TRUE) {
          rds_point_data$turbidity_mean <- rds_nn_summ$turbidity_mean
      }
      
        if (is.na(eval_criteria$rw_443) == TRUE) {
          rds_point_data$rw_443 <- rds_nn_summ$rw_443_mean
      }
      
         if (is.na(eval_criteria$rw_547) == TRUE) {
          rds_point_data$rw_547 <- rds_nn_summ$rw_547_mean
      }
      
      outer_template <- bind_rows(outer_template, rds_point_data)

    }
}
   return(outer_template)
}

###

cci_l_l <- list.files('cci_lakes_by_lake/', 
                            pattern = '*.rds',
                            full.names = TRUE,
                            recursive = TRUE)
### 

# Advesperascit

plan(callr, workers = 12)
options(future.globals.maxSize = 1.6e+10)

for (i in 1:10) {
  ival = eval(i)
  lake_rds <- read_rds(cci_l_l[ival])
  #lake_rds <- lake_rds %>% distinct(point_id, date, .keep_all = TRUE)
  filename <- paste0('cci_knn/', basename(cci_l_l[ival]))
  
  lake_filled_knn <- future_map(1:1827,
                          ~nn_filler(.x, rds_interior = lake_rds)) %>% 
    bind_rows()
  
  write_rds(lake_filled_knn, filename)
  print(paste('Completed:', cci_l_l[ival]))
  
}
  
# Revacholiere

plan(callr, workers = 12)
options(future.globals.maxSize = 1.6e+10)

for (i in 10:20) {
  ival = eval(i)
  lake_rds <- read_rds(cci_l_l[ival])
  #lake_rds <- lake_rds %>% distinct(point_id, date, .keep_all = TRUE)
  filename <- paste0('cci_knn/', basename(cci_l_l[ival]))
  
  lake_filled_knn <- future_map(1:1827,
                          ~nn_filler(.x, rds_interior = lake_rds)) %>% 
    bind_rows()
  
  write_rds(lake_filled_knn, filename)
  print(paste('Completed:', cci_l_l[ival]))
  
}

# Florilegium

plan(callr, workers = 10)
options(future.globals.maxSize = 1.6e+10)

for (i in 20:30) {
  ival = eval(i)
  lake_rds <- read_rds(cci_l_l[ival])
  #lake_rds <- lake_rds %>% distinct(point_id, date, .keep_all = TRUE)
  filename <- paste0('cci_knn/', basename(cci_l_l[ival]))
  
  lake_filled_knn <- future_map(1:1827,
                          ~nn_filler(.x, rds_interior = lake_rds)) %>% 
    bind_rows()
  
  write_rds(lake_filled_knn, filename)
  print(paste('Completed:', cci_l_l[ival]))
  
}

# Cognoscere

plan(callr, workers = 15)
options(future.globals.maxSize = 1.6e+10)

for (i in 30:40) {
  ival = eval(i)
  lake_rds <- read_rds(cci_l_l[ival])
  #lake_rds <- lake_rds %>% distinct(point_id, date, .keep_all = TRUE)
  filename <- paste0('cci_knn/', basename(cci_l_l[ival]))
  
  lake_filled_knn <- future_map(1:1827,
                          ~nn_filler(.x, rds_interior = lake_rds)) %>% 
    bind_rows()
  
  write_rds(lake_filled_knn, filename)
  print(paste('Completed:', cci_l_l[ival]))
  
}


# Second pass, using imputeTS


cci_knn <- list.files('cci_knn/', 
                            pattern = '*.rds',
                            full.names = TRUE,
                            recursive = TRUE)


for (i in 1:length(cci_knn)) {
  ###
  
  ival <- eval(i)
  
  int_slice <- readRDS(cci_knn[ival]) 
  
  ##
  
  int_slice_points <- unique(int_slice$point_id)
  
  int_slice_length <- length(int_slice_points)
  
  ##

  chla <- int_slice %>% 
    select(x, y, point_id, date, chla_mean)
  
  temp <- int_slice %>% 
    select(x, y, point_id, date, lake_surface_water_temperature)
  
  turb <- int_slice %>% 
    select(x, y, point_id, point_id, date, turbidity_mean)
  
  date_frame <- int_slice %>% 
    select(-chla_mean, -lake_surface_water_temperature, -turbidity_mean)
  
  ##
  
  chla <- chla %>% 
    group_by(x, y) %>% 
    group_modify(~ as.data.frame(na_interpolation(.x)),
                 option = 'stine')
  
  temp <- temp %>% 
    group_by(x, y) %>% 
    group_modify(~ as.data.frame(na_interpolation(.x)),
                 option = 'stine') 
  
  turb <- turb %>% 
    group_by(x, y) %>% 
    group_modify(~ as.data.frame(na_interpolation(.x)),
                 option = 'stine')

  assembly_frame <- left_join(date_frame, chla)
  
  assembly_frame <- left_join(assembly_frame, temp)
  
  assembly_frame <- left_join(assembly_frame, turb)
  
  ##
  
  filename <- paste0('cci_interpolated/', basename(cci_knn[ival]))
  
  write_rds(assembly_frame, filename)
  
  print(paste('Completed:', ival, 'of', length(cci_knn)))
}


ok <- readRDS('cci_interpolated/cci_okanagan.rds') %>% 
  select(x, y, date, chla_mean, turbidity_mean, lake_surface_water_temperature)

```

#5.) Import calcium data, interpolate

```{r}

### Generate North America subset CCI data

cci_lakes_shapefile <- read_sf('auxiliary_files/cci_lakes_shapefile.gpkg') %>% 
  st_transform(st_crs(4087))

na_bbox <- read_sf('auxiliary_files/north_america_bbox.gpkg') %>% 
  st_transform(st_crs(4087))

bc_bbox <- read_sf('auxiliary_files/bc_bbox.gpkg') %>% 
  st_transform(st_crs(4087))

cci_lakes_north_america <- st_intersection(cci_lakes_shapefile, na_bbox)%>% 
  select(id, name) %>% 
  mutate(area = st_area(geom))

cci_lakes_north_america$area <- as.numeric(cci_lakes_north_america$area)

cci_lakes_north_america <- cci_lakes_north_america %>% 
  mutate(area_km = area/1000000)

cci_lakes_bc <- st_intersection(cci_lakes_shapefile, bc_bbox) %>% 
  select(id, name) %>% 
  mutate(area = st_area(geom))

cci_lakes_bc$area <- as.numeric(cci_lakes_bc$area)

cci_lakes_bc <- cci_lakes_bc %>% 
  mutate(area_km = area/1000000)

### import Guerin et al 2024 data

calcium_data <- read_csv('downloads/guerin_et_al_2024_data/dryad/site-date_calcium_985955.csv') %>% 
  st_as_sf(coords = c('LONGITUDE', 'LATITUDE'),
           crs = 4326) %>% 
  st_transform(crs = 4087)

calcium_data_filtered <- calcium_data %>% 
  select(DATE, UNITS, MEAN) %>% 
  rename(date = DATE,
         units = UNITS,
         mean = MEAN) %>% 
    st_intersection(cci_lakes_north_america) %>% 
      mutate(x = sf::st_coordinates(.)[,1],
                y = sf::st_coordinates(.)[,2]) %>% 
  st_drop_geometry() %>% 
  filter(date > dmy('01-01-2002'))

###

calcium_data_filtered_bc <- calcium_data %>% 
  select(DATE, UNITS, MEAN) %>% 
  rename(date = DATE,
         units = UNITS,
         mean = MEAN) %>% 
    st_intersection(cci_lakes_bc) %>% 
      mutate(x = sf::st_coordinates(.)[,1],
                y = sf::st_coordinates(.)[,2]) %>% 
  filter(date > dmy('01-01-2016'))

### Generate list of CCI lakes with corresponding Guerin data

cci_attached <- st_join(cci_lakes_north_america, calcium_data)

calcium_matched_cci <- unique(cci_attached$name)

cci_lakes_poly_matched <- cci_lakes_north_america %>% 
  filter(name %in% calcium_matched_cci) %>% 
  select(id, name)

#write_sf(cci_lakes_poly_matched, 'auxiliary_files/cci_lakes_calcium_match.gpkg')

## Retrieve assembly frame

cci_assembly <- list.files('cci_interpolated/', 
                            pattern = '*.rds',
                            full.names = TRUE,
                            recursive = TRUE)

outer_frame <- tibble(point_id = numeric(),
                      x = numeric(),
                      y = numeric())

for (i in 1:length(cci_assembly)) {
  ival = eval(i)
  int_assembly <- read_rds(cci_assembly[ival]) %>% 
    select(x, y, point_id) %>% 
    distinct(point_id, .keep_all = TRUE)
  outer_frame <- bind_rows(outer_frame, int_assembly)
  print(paste('Completed:', ival, 'of', length(cci_assembly)))
}

outer_frame_sf <- outer_frame %>% st_as_sf(coords = c('x', 'y'),
                                           crs = 4087) %>% 
  select(-x, -y)

bc_joined_calcium <- st_join(calcium_data_filtered_bc, outer_frame_sf, 
                             join = st_nearest_feature) %>% 
  select(date, units, mean, area_km, point_id) %>% 
  st_drop_geometry() %>% 
  rowid_to_column('calcium_observation_id')

###

cci_data <- list.files('cci_interpolated/', 
                            pattern = '*.rds',
                            full.names = TRUE,
                            recursive = TRUE) 

cci_data_collated <- lapply(cci_data, readRDS) %>% 
  bind_rows()

cci_calcium_joined <- left_join(cci_data_collated, bc_joined_calcium,
                                by = c('point_id', 'date')) 
#write_rds(cci_calcium_joined, 'auxiliary_files/cci_calcium_joined.rds')



```

## GAM

```{r}

cci_calcium_joined <- read_rds('auxiliary_files/cci_calcium_joined.rds') %>% 
  select(x, y, date, turbidity_mean, mean, units, area_km)

```

# 6.) Suitability modeling

# 7.) Suitability composition modeling

# ~~ Supplemental

## Process continental data for calcium

```{r}

  cci_lakes_calcium_matchup_polygon <- read_sf('auxiliary_files/cci_calcium_matchup_polygon.gpkg')


  cci_slices <- list.files('cci_lakes_slices/', 
                            pattern = '*.rds',
                            full.names = TRUE,
                            recursive = TRUE)
  
  test_rds <- read_rds(cci_slices[1])

  
### Updated downloads
  
path = '/home/steven/Downloads/cci_lakes_download/'

###

prefix_template <- 'https://dap.ceda.ac.uk/neodc/esacci/lakes/data/lake_products/L3S/v2.1/merged_product/'

suffix_template_a <- 'ESACCI-LAKES-L3S-LK_PRODUCTS-MERGED-'

suffix_template_b <- '-fv2.1.0.nc'

###

year_list <- c('2002', '2003', '2004', '2005', '2006', '2007', '2008', 
               '2009', '2010', '2011', '2012', '2013', '2014', '2015', 
               '2016', '2017', '2018', '2019', '2020')

month_list <- c('01', '02', '03', '04', '05', '06', '07', '08', '09', '10', '11', '12')

month_daylengths <- c(31, 28, 31, 30, 31, 30, 31, 31, 30, 31, 30, 31)

day_list <- c( '01',  '02',  '03',  '04',  '05',  '06',  '07',  '08',  '09', 
               '10', '11', '12', '13',  '14', '15', '16', '17', '18', '19', 
               '20',  '21', '22', '23', '24', '25', '26', '27', '28', '29', 
               '30', '31')

comb_date <- paste0(year_list[1], month_list[1], day_list[1])

date_dir <- paste0(year_list[1], '/', month_list[1], '/')

options(timeout = 1000)

for (i in 4:19) {
  ival <- eval(i)
  
  interior_year <- year_list[ival]
  
  for (j in 1:12) {
    jval <- eval(j)
    
    interior_month <- month_list[jval]
    
    interior_day_length <- month_daylengths[jval]
    
    if (interior_month == '02' & interior_year == '2004') {
      interior_day_length <- 29
      print('Leap year!')
    } 
    
    if (interior_month == '02' & interior_year == '2008') {
      interior_day_length <- 29
      print('Leap year!')
    } 
    
    if (interior_month == '02' & interior_year == '2012') {
      interior_day_length <- 29
      print('Leap year!')
    } 
    
    if (interior_month == '02' & interior_year == '2016') {
      interior_day_length <- 29
      print('Leap year!')
    } 
    
    if (interior_month == '02' & interior_year == '2020') {
      interior_day_length <- 29
      print('Leap year!')
    }

    for (k in 1:interior_day_length) {
      kval <- eval(k)
      
      interior_day <- day_list[kval]
      
      comb_date <- paste0(interior_year,  interior_month, interior_day )
      
      date_dir <- paste0(interior_year, '/', interior_month , '/')
      
      filename <- paste0(prefix_template, date_dir, suffix_template_a, comb_date,
                              suffix_template_b)

      download.file(filename, paste0(path, basename(filename)))
      
      print(paste('Completed:', filename))
      
      Sys.sleep(5)
      
    }
    
  }
  
}

  
  
  

```

## Temperature data

```{r}

# Auxiliary files

cci_lakes_shapefile <- read_sf('auxiliary_files/cci_lakes_shapefile.gpkg') %>% 
  st_transform(st_crs(4087))

bc_bbox <- read_sf('auxiliary_files/bc_bbox.gpkg') %>% 
  st_transform(st_crs(4087))

cci_lakes_bc <- st_intersection(cci_lakes_shapefile, bc_bbox) %>% 
  select(id, name) %>% 
  st_transform(crs = 3005)


### EMS data

ems_lake_data <- list.files(path = 'downloads/in_situ_measurements/bc_lake_monitoring_program/lake_monitoring_raw_data/', 
                            pattern = '*.csv', 
                            full.names = TRUE) %>% 
  lapply(read_csv, col_select = c(PARAMETER, 
                                  COLLECTION_START,
                                  RESULT,
                                  UNIT,
                                  UPPER_DEPTH,
                                  LOWER_DEPTH,
                                  Level,
                                  depthsUploaded,
                                  Latitude,
                                  Longitude,
                                  WSGZTTDNM,)) %>% 
  bind_rows()

ems_lake_data <- ems_lake_data %>% mutate(id = rownames(ems_lake_data))

# Correct missing negative sign in longitude data in Shuswap Lake sites

ems_lake_data <- ems_lake_data %>% mutate(Longitude = -1*abs(Longitude))

ems_sf <- st_as_sf(ems_lake_data, 
                   coords = c('Longitude', 'Latitude'),
                   crs = 4326)

###

# Filter variables of interest

ems_vars <- ems_sf %>% filter(PARAMETER == 'Temperature-Field')

# Retrieve epilimnion results

ems_vars <- ems_vars %>% filter(Level == 'Epilimnion')

ems_vars <- ems_vars %>% 
  st_transform(crs = st_crs(3005)) %>% 
  st_intersection(cci_lakes_bc)

ems_vars <- ems_vars %>% select(PARAMETER, COLLECTION_START, RESULT)



temp_metadata <- list.files('downloads/sorensen_et_al_2024/in_situ_lake_temps/in_situ_published/final_data//', 
                            pattern = '_metadata.csv',
                            full.names = TRUE,
                            recursive = TRUE)
  
prefix_list <- c('CHA', 'CLE', 'DEV', 'FLA', 'GSL', 'HOU', 'LEW', 'MAL', 'MAR',
                 'MCC', 'MEA', 'MEN', 'MON', 'OKE', 'ONE', 'PON', 'PYR', 'RED',
                 'SAK', 'SEB', 'SEN', 'TAH', 'TAW', 'UPK', 'UTA', 'WAL', 'WAS',
                 'WIN', 'WIP')


```

